Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
check

@@

\begin{definition}[Cast Abstract Data Type (Cast ADT)]
	\label{def:cast-rep}
	A cast abstract data type is a set $ Cast $, which is indexed by two types, 
	with four operators:
	\begin{description}
		\item[$ id(T) = c $] constructs an cast from a type
%		, where $ c : T 
%		\Longrightarrow T $
		\item[$ seq(c_1,c_2)=c $] composes two casts
%		, where $ 
%		\judgeTypeFT{c_1}{T_1}{T_2} $, $ \judgeTypeFT{c_2}{T_2}{T_3} $, and $ 
%		\judgeTypeFT{c}{T_1}{T_3} $
		\item[$ cast(T_1,l,T_2)=c $] constructs a cast from $ T_1 $ to $ T_2 $
		\item[$ applyCast(v,c)=r $] applies a cast onto a value
	\end{description}
	We denote by $ c : T_1 \Longrightarrow T_2 $ to mean $ c $ is in $ Cast \; 
	T_1 \; T_2 $. And we say ``$ c $ is from $ T_1 $ to $ T_2 $''.
\end{definition}

@@

\todo[inline]{An extra property is required after changing case to small-step 
-KC}
\begin{lemma}[$ \text{Lazy D Cast ADT} \cap \text{Monoid} $ Respects 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
	\lazyD{} Cast ADT and a monoid,
	\[
	\text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
	\]
\end{lemma}
\begin{proof}Proving left implies right is trivial.
To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
\end{proof}

>>>>

We start by defining a CEK machine \effCEK{C} that is parameterized
over the cast representation $C$. This machine is space efficient
provided that the cast representation performs compression.  The
interface between the machine and the cast representation is defined
by an abstract data type, named Cast ADT, that we define shortly.
%

\todo[inline]{UNDER CONSTRUCTION. -JS}

@@

\begin{definition}[Cast Abstract Data Type (Cast ADT)]
	\label{def:cast-rep}
	A cast abstract data type is a set $Cast $, which is indexed by two types, 
	with four operators:
	\begin{description}
		\item[$id(T) $] constructs an cast from a type
%		, where $c : T 
%		\Longrightarrow T $
		\item[$seq(c_1,c_2) $] composes two casts
%		, where $
%		\judgeTypeFT{c_1}{T_1}{T_2} $, $\judgeTypeFT{c_2}{T_2}{T_3} $, and $
%		\judgeTypeFT{c}{T_1}{T_3} $
		\item[$cast(T_1,l,T_2) $] constructs a cast from $T_1$ to $T_2$
		\item[$ applyCast(v,c)=r $] applies a cast onto a value
	\end{description}
	We denote by $c : T_1 \Longrightarrow T_2 $ to mean $ c $ is in $ Cast \; 
	T_1 \; T_2 $. And we say ``$ c $ is from $ T_1 $ to $ T_2 $''.
\end{definition}

@@

\todo[inline]{An extra property is required after changing case to small-step 
-KC}
\begin{proposition}[Correctness of \effCEK{C}]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
	\lazyD{} Cast ADT and a monoid,
	\[
	\text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
	\]
\end{proposition}
\begin{proof}Proving left implies right is trivial.
To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
\end{proof}
